Results

### 2019-08-14 analysis/03_analysis.Rmd
Updated marginal posterior plots

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 1000)

@@

```{r plot-marginals}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 1 # + Demographics

@@

    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No"

@@

    "Religion: Catholic to Atheist"

@@

    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: Yes to No", "Volunteer frequency: Weekly to Every few years",

@@

    "Gender: Male to Prefer not to say", "Marital status: Married to Never married", "Education: Less than high school to Doctorate",

@@

    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: Yes to No",

@@

    "Religion: Catholic to Atheist",

@@

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels") +
    facet_wrap(~ levels, ncol = 5)
}

# Save plot
if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
ggsave(
  file_name,
  path = here::here("analysis", "output", "figures"),
  width = 20, height = 20, units = "in"
)
```

>>>>

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

@@

```{r plot-marginals}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No"

@@

      "Religion: ", 
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")

@@

    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",

@@

      "Gender: ", 
      c("Female", "Transgender", "Prefer not to say", "Other")
      "Marital status: ", 
      c("Widowed", "Divorced", "Separated", "Never married")
    "Education: Less than high school to Doctorate",

@@

    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",

@@

      "Religion: ", 
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")

@@

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Covariates") +
    facet_wrap(~ levels, ncol = 5)
}

# Save plot
if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
ggsave(
  file_name,
  path = here::here("analysis", "output", "figures"),
  width = ifelse(intercept == 1, 12, 20), 
  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
  units = "in"
)
```
